Stage-Splitting a Modal Language

### 2014-08-12 paper/semantics.tex
added more text to splitting
fixing up metatheory

\section{The \lang\ Language}

@@

\begin{definition}
Contexts $\Gamma$ is well-formed ($\Gamma\wf$) if it
contains only stage-2 variables.
\end{definition}

\begin{definition}
An environment $\xi$ is well-formed ($\Gamma\vdash\xi\wf$) if either:
\begin{enumerate}
\item $\xi = \cdot$; or
\item $\xi = \xi',x\mapsto e$ where
$\Gamma\vdash\xi'\wf$ and
$\Gamma,\dom{\xi'}\vdash \coltwo{e}{B}$ and
$\Gamma,\dom{\xi'}\vdash e \res$.
\end{enumerate}
\end{definition}

\begin{theorem}
If $\typesone e A$ then $\Gamma\wf$ and $A\istypeone$.
\end{theorem}

@@

\begin{theorem}
If $\diatwosub$ and $\typestwo e A$ then
\begin{enumerate}
\item $\Gamma\vdash \coltwo{q}{A}$; and
\item $\Gamma\vdash q\val$.
\end{enumerate}
\end{theorem}

>>>>

\section{The \lang\ Language}
\label{sec:semantics}

@@

\TODO explain that the $\vdash_\bbtwo$ judgments are for \langTwo.

%\begin{definition}
%Context $\Gamma$ is well-formed ($\Gamma\wf$) if it
%contains only stage-2 variables.
%\end{definition}

\begin{definition}
An environment $\xi$ is well-formed ($\Gamma\vdash\xi\wf$) if either:
\begin{enumerate}
\item $\xi = \cdot$; or
\item $\xi = \xi',x:B\mapsto e$ where
$\Gamma\vdash\xi'\wf$ and
$\typeslangTwo[\Gamma,\dom{\xi'}] e B$
%$\Gamma,\dom{\xi'}\vdash \coltwo{e}{B}$ and
%$\Gamma,\dom{\xi'}\vdash e \res$.
\end{enumerate}
\end{definition}

\begin{theorem}
If $\typeswor e A$ then $\Gamma\wf$ and $A\istypewor$.
\end{theorem}

@@

\begin{theorem}
If $\diatwosub$ and $\typestwo e A$ then
\begin{enumerate}
\item $\typeslangTwo q A$; and
\item $\Gamma\vdash_\bbtwo q\val$.
\end{enumerate}
\end{theorem}

\TODO fix the next theorem:

\begin{theorem}
If $\Gamma\vdash\xi\wf$ and
$\Gamma,\dom\xi\vdash \colone{v}{A}$ and
$\Gamma,\dom\xi\vdash v\pval$
then 
$\reify{\xi}{v}{q}$ and
$\typeslangTwo q A$.
\end{theorem}
